% SPDX-FileCopyrightText: 2026 IObundle, Lda
%
% SPDX-License-Identifier: MIT
%
% Py2HWSW Version 0.81 has generated this code (https://github.com/IObundle/py2hwsw).

axi\_araddr\_o & output & AXI\_ADDR\_W & AXI address read channel byte address. \\* \nobreakhline
\rowcolor{iob-blue}
axi\_arvalid\_o & output & 1 & AXI address read channel valid. \\* \nobreakhline
axi\_arready\_i & input & 1 & AXI address read channel ready. \\* \nobreakhline
\rowcolor{iob-blue}
axi\_rdata\_i & input & AXI\_DATA\_W & AXI read channel data. \\ \hline
axi\_rresp\_i & input & 2 & AXI read channel response. \\ \hline
\rowcolor{iob-blue}
axi\_rvalid\_i & input & 1 & AXI read channel valid. \\ \hline
axi\_rready\_o & output & 1 & AXI read channel ready. \\ \hline
\rowcolor{iob-blue}
axi\_arid\_o & output & AXI\_ID\_W & AXI address read channel ID. \\ \hline
axi\_arlen\_o & output & AXI\_LEN\_W & AXI address read channel burst length. \\ \hline
\rowcolor{iob-blue}
axi\_arsize\_o & output & 3 & AXI address read channel burst size. \\ \hline
axi\_arburst\_o & output & 2 & AXI address read channel burst type. \\ \hline
\rowcolor{iob-blue}
axi\_arlock\_o & output & 2 & AXI address read channel lock type. \\ \hline
axi\_arcache\_o & output & 4 & AXI address read channel memory type. \\ \hline
\rowcolor{iob-blue}
axi\_arqos\_o & output & 4 & AXI address read channel quality of service. \\ \hline
axi\_rid\_i & input & AXI\_ID\_W & AXI Read channel ID. \\ \hline
\rowcolor{iob-blue}
axi\_rlast\_i & input & 1 & AXI Read channel last word. \\ \hline
axi\_awaddr\_o & output & AXI\_ADDR\_W & AXI address write channel byte address. \\ \hline
\rowcolor{iob-blue}
axi\_awvalid\_o & output & 1 & AXI address write channel valid. \\ \hline
axi\_awready\_i & input & 1 & AXI address write channel ready. \\ \hline
\rowcolor{iob-blue}
axi\_wdata\_o & output & AXI\_DATA\_W & AXI write channel data. \\ \hline
axi\_wstrb\_o & output & AXI\_DATA\_W/8 & AXI write channel write strobe. \\ \hline
\rowcolor{iob-blue}
axi\_wvalid\_o & output & 1 & AXI write channel valid. \\ \hline
axi\_wready\_i & input & 1 & AXI write channel ready. \\ \hline
\rowcolor{iob-blue}
axi\_bresp\_i & input & 2 & AXI write response channel response. \\ \hline
axi\_bvalid\_i & input & 1 & AXI write response channel valid. \\ \hline
\rowcolor{iob-blue}
axi\_bready\_o & output & 1 & AXI write response channel ready. \\ \hline
axi\_awid\_o & output & AXI\_ID\_W & AXI address write channel ID. \\ \hline
\rowcolor{iob-blue}
axi\_awlen\_o & output & AXI\_LEN\_W & AXI address write channel burst length. \\ \hline
axi\_awsize\_o & output & 3 & AXI address write channel burst size. \\ \hline
\rowcolor{iob-blue}
axi\_awburst\_o & output & 2 & AXI address write channel burst type. \\ \hline
axi\_awlock\_o & output & 2 & AXI address write channel lock type. \\ \hline
\rowcolor{iob-blue}
axi\_awcache\_o & output & 4 & AXI address write channel memory type. \\ \hline
axi\_awqos\_o & output & 4 & AXI address write channel quality of service. \\ \hline
\rowcolor{iob-blue}
axi\_wlast\_o & output & 1 & AXI Write channel last word flag. \\ \hline
axi\_bid\_i & input & AXI\_ID\_W & AXI Write response channel ID. \\
