% SPDX-FileCopyrightText: 2026 IObundle, Lda
%
% SPDX-License-Identifier: MIT
%
% Py2HWSW Version 0.81 has generated this code (https://github.com/IObundle/py2hwsw).

csrs\_axil\_araddr\_i & input & 12 & AXI-Lite address read channel byte address. \\* \nobreakhline
\rowcolor{iob-blue}
csrs\_axil\_arvalid\_i & input & 1 & AXI-Lite address read channel valid. \\* \nobreakhline
csrs\_axil\_arready\_o & output & 1 & AXI-Lite address read channel ready. \\* \nobreakhline
\rowcolor{iob-blue}
csrs\_axil\_rdata\_o & output & DATA\_W & AXI-Lite read channel data. \\ \hline
csrs\_axil\_rresp\_o & output & 2 & AXI-Lite read channel response. \\ \hline
\rowcolor{iob-blue}
csrs\_axil\_rvalid\_o & output & 1 & AXI-Lite read channel valid. \\ \hline
csrs\_axil\_rready\_i & input & 1 & AXI-Lite read channel ready. \\ \hline
\rowcolor{iob-blue}
csrs\_axil\_awaddr\_i & input & 12 & AXI-Lite address write channel byte address. \\ \hline
csrs\_axil\_awvalid\_i & input & 1 & AXI-Lite address write channel valid. \\ \hline
\rowcolor{iob-blue}
csrs\_axil\_awready\_o & output & 1 & AXI-Lite address write channel ready. \\ \hline
csrs\_axil\_wdata\_i & input & DATA\_W & AXI-Lite write channel data. \\ \hline
\rowcolor{iob-blue}
csrs\_axil\_wstrb\_i & input & DATA\_W/8 & AXI-Lite write channel write strobe. \\ \hline
csrs\_axil\_wvalid\_i & input & 1 & AXI-Lite write channel valid. \\ \hline
\rowcolor{iob-blue}
csrs\_axil\_wready\_o & output & 1 & AXI-Lite write channel ready. \\ \hline
csrs\_axil\_bresp\_o & output & 2 & AXI-Lite write response channel response. \\ \hline
\rowcolor{iob-blue}
csrs\_axil\_bvalid\_o & output & 1 & AXI-Lite write response channel valid. \\ \hline
csrs\_axil\_bready\_i & input & 1 & AXI-Lite write response channel ready. \\
