% SPDX-FileCopyrightText: 2026 IObundle, Lda
%
% SPDX-License-Identifier: MIT
%
% Py2HWSW Version 0.81 has generated this code (https://github.com/IObundle/py2hwsw).

csrs & The Control and Status Register block contains registers accessible by the software for controlling the IP core attached as a peripheral. \\* \nobreakhline
\rowcolor{iob-blue}
phy\_reset\_counter & Counter to generate initial PHY reset signal. Configurable duration based on counter reset value. \\* \nobreakhline
cdc & Clock domain crossing block, using internal synchronizers. \\* \nobreakhline
\rowcolor{iob-blue}
transmitter & Ethernet transmitter that reads payload bytes from a host interface, emits preamble/SFD and payload, computes and appends the CRC, and provides flow-control so the surrounding logic knows when the transmitter is ready for the next frame. \\ \hline
receiver & Ethernet receiver that detects frame start, captures the destination MAC and payload, writes received bytes to a host interface, and validates the frame with a CRC check; it produces a ready/received indication for higher-level logic. \\ \hline
\rowcolor{iob-blue}
tx\_buffer & Buffer memory for data to be transmitted. \\ \hline
rx\_buffer & Buffer memory for data received. \\ \hline
\rowcolor{iob-blue}
buffer\_descriptors & Buffer descriptors memory. \\ \hline
data\_transfer & Manages data transfers between ethernet modules and interfaces. \\ \hline
\rowcolor{iob-blue}
mii\_management & Controls MII management signals. \\ \hline
eth\_logic & Extra ethernet logic for interface between CSRs and Data Transfer block. \\
